---
title: "EDA MERFISH Fetal Liver"
---

# Set up

Messages will be hidden and the output collapsed to make the Rmd more clear.

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/Saez/workflowr_projects/benchmark")
```

Loaded Packages.

```{r}
suppressPackageStartupMessages(library(mistyR))
suppressPackageStartupMessages(library(future))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(R.matlab))
plan("multisession", workers=12)
```

# Introduction

The data originate from the following study: 

Lu, Y. et al. Spatial transcriptome profiling by MERFISH reveals fetal liver 
hematopoietic stem cell niche architecture. Cell Discov 7, 47 (2021).

# WT Data

## Gene Information

```{r}
gene.tibble <- readxl::read_xlsx(
  "/home/philipp/data/saez/merfish/Supplement/41421_2021_266_MOESM1_ESM.xlsx", 
  skip = 1
  )
genes <- gene.tibble$`Gene name`
gene.tibble %>% slice_head(n=6)
```

## Cell Data

Raw Data:

```{r}
wt.samples <- list.files("/home/philipp/data/saez/merfish/Data/WT CellList")
sample.names <- str_extract(wt.samples, "CellID_[0-9]+")

if ("merfish.raw.data.RDS" %in% list.files("data/merfish_benchmark")) {
  raw.data <- readRDS("data/merfish_benchmark/merfish.raw.data.RDS")
} else {

  raw.data <- map(wt.samples, function(file) {
  readMat(paste0("/home/philipp/data/saez/merfish/Data/WT CellList/",
                             file))$CellList
  }) %>% setNames(sample.names)
  
  saveRDS(raw.data, "data/merfish_benchmark/merfish.raw.data.RDS")
}
```

```{r}
sample.names
```

Cell Metadata:

```{r}
cell.data <- map(raw.data, function(smp.data) {
  smp.cell.data <- map_dfr(seq.int(1, dim(smp.data)[3]), function(i) {
    cell_i <- smp.data[1:8, 1, i]
    tibble::tibble(id = cell_i$CellID, fov = cell_i$FOV, x = cell_i$Center[1, 1],
                   y = cell_i$Center[1, 2], total.rna.copy = cell_i$TotalRNACopyNumber[1, 1], 
           edge = cell_i$OnEdge[1, 1], type = cell_i$CellType, num.pixel = dim(cell_i$PixelList)[1])
  })
}) %>% setNames(sample.names)
```

```{r}
cell.data$CellID_190411 %>% slice_head(n=6)

#cell.data$CellID_190411 %>% distinct(fov, .keep_all= TRUE)

#cell.data$CellID_190411 %>% group_by(fov) %>% count
```

Merging Cell Data

```{r}
cell.meta <- cell.data %>% map2_dfr(names(cell.data), function(smp.data, name) {
  smp.data %>% mutate(sample = name)
}) %>%
  mutate(type_name = case_when(
  type == 1 ~ "Arterial.Endothelial.Cells",
  type == 2 ~ "Sinusoidal.Endothelial.Cells", 
  type == 3 ~ "Megakaryocytes",
  type == 4 ~ "Hepatocyte",
  type == 5 ~ "Macrophage",
  type == 6 ~ "Myeloid",
  type == 7 ~ "Erythroid.Progenitor",
  type == 8 ~ "Erythroid.Cell",
  type == 9 ~ "Unknown"
))
cell.meta %>% slice_head(n=6)
```

Expression Data:

```{r}
expr.data <- map(raw.data, function(smp.data) {
  smp.expr.data <- map_dfr(seq.int(1, dim(smp.data)[3]), function(i) {
    cell_i <- smp.data[1:8, 1, i]
    cell_i$CellID
    expr <- cell_i$RNACopyNumber %>% as.vector
    names(expr) <- genes
    c(id = cell_i$CellID, expr)
  })
})
```

```{r}
expr.data$CellID_190411 %>% slice_head(n=6)
```

Normalizing the expression data.

We divide each count by the sum of counts in the cell and then multiply by 1000
(just as they did it in the paper).

```{r}
expr.data.norm <- map(expr.data, function(sample) {
  cell.totals <- sample %>%
    pivot_longer(cols = 2:141) %>%
    group_by(id) %>%
    summarise(cell.sum = sum(value))
  
  sample %>%
    left_join(cell.totals, by="id") %>%
    pivot_longer(cols = 2:141) %>%
    mutate(normalized = value / cell.sum * 1000) %>%
    select(-c(cell.sum, value)) %>%
    pivot_wider(names_from = name, values_from = normalized)
})
```

```{r}
expr.data.norm$CellID_190411 %>% slice_head(n = 6)
```

Looking at the distribution for the top 36 markers by sum of expression. And
even for these markers we mostly have zero counts.

```{r fig.width=14, fig.height=10}
expr.data$CellID_190411 %>%
  select(- id) %>%
  pivot_longer(cols = everything()) %>%
  group_by(name) %>%
  mutate(sum.marker = sum(value)) %>%
  ungroup() %>%
  slice_max(order_by = sum.marker, n = 23700*36) %>%
  ggplot() +
  geom_histogram(aes(value), bins = 30) +
  facet_wrap(~ name, ncol=6, nrow=6, scales="free")
```

Cell Types per Sample

```{r}
cell.meta %>%
  count(sample, type_name) %>%
  ggplot() +
  geom_bar(aes(y = type_name, x = n), stat="identity") +
  facet_wrap(~ sample) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

Visualization of a Part of the Sample

The visualization are now based on the assumption that the images are
1536 x 1536 (all these things were not quite documented at all!).

```{r}
if ("CellID_190411.pixels.RDS" %in% list.files("data/merfish_benchmark")) {
  CellID_190411.pixels <- readRDS("data/merfish_benchmark/CellID_190411.pixels.RDS")
} else {
  img.size <- 1536
  CellID_190411.pixels <- map_dfr(seq.int(1, dim(raw.data$CellID_190411)[3]), function(i) {
    cell_i <- raw.data$CellID_190411[1:8, 1, i]
    tibble::tibble(id = cell_i$CellID, type = cell_i$CellType, fov = cell_i$FOV, 
                   pixels = cell_i$PixelList)
  }) %>%
  mutate(type = factor(type)) %>%
  mutate(id = factor(id)) %>%
  mutate(y = pixels %% img.size, x = ceiling(pixels / img.size))
  
  saveRDS(CellID_190411.pixels, "data/merfish_benchmark/CellID_190411.pixels.RDS")
}
rm(raw.data)
```

Verification of the right image size.

Example field of view 5.

```{r}
CellID_190411.pixels %>%
  filter(fov == 5) %>%
  ggplot() +
  geom_point(aes(x=x, y=y, col=id), size=.1) +
  theme(legend.position = "none") +
  scale_color_manual(values=rep(c("dodgerblue", "brown", "purple", "blue",
                                  "seagreen", "gold", "tomato", "turquoise",
                                  "magenta", "springgreen"), 250)) +
  coord_equal()
```

Example field of view 1.

```{r}
CellID_190411.pixels %>%
  filter(fov == 1) %>%
  ggplot() +
  geom_point(aes(x=x, y=y, col=id), size=.1) +
  theme(legend.position = "none") +
  scale_color_manual(values=rep(c("dodgerblue", "brown", "purple", "blue",
                                  "seagreen", "gold", "tomato", "turquoise",
                                  "magenta", "springgreen"), 250)) +
  coord_equal()
```

Check wether the center of mass makes sense. It looks very good.

```{r}
center.mass <- cell.data$CellID_190411 %>%
  filter(fov == 5) %>%
  mutate(id = factor(id)) %>%
  mutate(center_x = x, center_y = y) %>%
  select(c(id, fov, center_x, center_y))

CellID_190411.pixels %>%
  filter(fov == 5) %>%
  left_join(center.mass, by="id") %>%
  ggplot() +
  geom_point(aes(x=x, y=y, col=id), size=.1, alpha=0.01) +
  geom_point(aes(x=center_x, y=center_y, col=id), size=2) +
  coord_equal()
```

Now the next question is, could we stitch together the images?

How many field of views do we have per sample? Looking at the maximum
index and the number of fovs which are present.

```{r}
cell.meta %>% group_by(sample) %>% distinct(fov, .keep_all = TRUE) %>%
  summarise(max(fov))

cell.meta %>% group_by(sample) %>% distinct(fov, .keep_all = TRUE) %>% 
  summarise(n())
```

Looking more closely at CellID_190411.

For example plot the first 4 fields of views in a row.

From looking at these images I would assume that we are looking at the left
side of the image actually. And thus we need to stitch along the y-axis.

```{r fig.width=16, fig.height=6}
CellID_190411.pixels %>%
  filter(fov %in% seq.int(0, 3)) %>%
  ggplot() +
  geom_point(aes(x=x, y=y, col=id), size=.1) +
  theme(legend.position = "none") +
  scale_color_manual(values=rep(c("dodgerblue", "brown", "purple", "blue",
                                  "seagreen", "gold", "tomato", "turquoise",
                                  "magenta", "springgreen"), 250)) +
  facet_wrap(~ fov, ncol=4) +
  coord_equal()
```

What if we look at last 4 fovs?

```{r fig.width=16, fig.height=6}
CellID_190411.pixels %>%
  filter(fov %in% seq.int(117, 120)) %>%
  ggplot() +
  geom_point(aes(x=x, y=y, col=id), size=.1) +
  theme(legend.position = "none") +
  scale_color_manual(values=rep(c("dodgerblue", "brown", "purple", "blue",
                                  "seagreen", "gold", "tomato", "turquoise",
                                  "magenta", "springgreen"), 250)) +
  facet_wrap(~ fov, ncol=4) +
  coord_equal()
```

So all in all I have no clue how I would have to stitch them together!

These are some hints from the Matlab code

```{r eval = FALSE}
ImageSize = 1536 # number of pxls
StepSize = 1394 # 150/0.1076
# overlap -> 142
XSteps = 13
YSteps = 15
EndFrame = 40
StartFrame =18
NFOV = 144 # number of fields of views
```

If there is in fact a certain overlap between the images I would assume
that we have the same cell ID in different field of views. Is this true?

No each cell ID is only in one field of view. Still this could be an artifact
of removing all cell which were on the edge from the data.

```{r}
cell.data$CellID_190411 %>% 
  group_by(id) %>% 
  summarise(n = length(unique(fov))) %>%
  summary(n)
```

We could assume one model for the first sample where we move the microscope 
from bottom left to the top, go back, one to the right and to the top again.

This could be reasonable, but it is quite impossible to say wether it is right.

```{r fig.width=16, fig.height=16}
xsteps <- 11

fovs <- CellID_190411.pixels$fov %>% unique %>% as.vector()
#fovs

model_1 <- fovs %>% map_dfr(function(fov) {
  y <- floor(fov / xsteps)
  x <- fov - y*xsteps
  tibble::tibble(fov = fov, xstep = x, ystep = y)
})
#model_1

xdict <- model_1$xstep %>% setNames(model_1$fov)
ydict <- model_1$ystep %>% setNames(model_1$fov)

# now I need to add values to the x and y coordinates based on the steps
# (where in the global image we are)
ImageSize = 1536
StepSize = 1394

subsampled <- sample(1:nrow(CellID_190411.pixels), 0.01*nrow(CellID_190411.pixels))

#test <- CellID_190411.pixels %>%
#  slice(subsampled) %>%
#  rowwise() %>%
#  mutate(newx = x + xdict[fov]*StepSize,
#         newy = y + ydict[fov]*StepSize)

# use some vectorized approch to deal with the pixels.

prep <- CellID_190411.pixels %>%
  slice(subsampled)

# checke whether we have all
#prep$fov %>% unique() %>% sort == names(xdict) %>% as.numeric() %>% sort

sx <- xdict[prep$fov %>% as.character]
sy <- ydict[prep$fov %>% as.character]

test <- cbind(prep, sx, sy) %>%
  mutate(
    newx = x + sx*StepSize,
    newy = y + sy*StepSize
  )

test %>%
  ggplot() +
  geom_point(aes(x = newx, y=newy, col=type), size=.1) +
  #theme(legend.position = "none") +
  scale_color_manual(values=rep(c("dodgerblue", "brown", "purple", "blue",
                                  "seagreen", "gold", "tomato", "turquoise",
                                  "magenta", "springgreen"), 1000000)) +
  coord_equal() +
  scale_x_continuous(name="Speed of cars", limits=c(0, 16000), breaks = )
```

What about another test if we change x and y.

This just looks super wrong!

```{r fig.width=16, fig.height=16}
xsteps <- 11

fovs <- CellID_190411.pixels$fov %>% unique %>% as.vector()
#fovs

model_1 <- fovs %>% map_dfr(function(fov) {
  x <- floor(fov / xsteps)
  y <- fov - x*xsteps
  tibble::tibble(fov = fov, xstep = x, ystep = y)
})
#model_1

xdict <- model_1$xstep %>% setNames(model_1$fov)
ydict <- model_1$ystep %>% setNames(model_1$fov)

# now I need to add values to the x and y coordinates based on the steps
# (where in the global image we are)
ImageSize = 1536
StepSize = 1394

subsampled <- sample(1:nrow(CellID_190411.pixels), 0.01*nrow(CellID_190411.pixels))

#test <- CellID_190411.pixels %>%
#  slice(subsampled) %>%
#  rowwise() %>%
#  mutate(newx = x + xdict[fov]*StepSize,
#         newy = y + ydict[fov]*StepSize)

# use some vectorized approch to deal with the pixels.

prep <- CellID_190411.pixels %>%
  slice(subsampled)

# checke whether we have all
#prep$fov %>% unique() %>% sort == names(xdict) %>% as.numeric() %>% sort

sx <- xdict[prep$fov %>% as.character]
sy <- ydict[prep$fov %>% as.character]

test <- cbind(prep, sx, sy) %>%
  mutate(
    newx = x + sx*StepSize,
    newy = y + sy*StepSize
  )

test %>%
  ggplot() +
  geom_point(aes(x = newx, y=newy, col=type), size=.1) +
  #theme(legend.position = "none") +
  scale_color_manual(values=rep(c("dodgerblue", "brown", "purple", "blue",
                                  "seagreen", "gold", "tomato", "turquoise",
                                  "magenta", "springgreen"), 1000000)) +
  coord_equal()
```

# MISTy views

Since once cannot really say how and whether it makes sense to stitch those
images together, we will run MISTy on each sample on each field of view.

But first we will remove all the FOVs which have too few cells.

```{r}
map2_dfr(cell.data, names(cell.data), function(smp, name) {
  smp %>%
    group_by(fov) %>%
    summarise(n = n()) %>%
    mutate(sample = name)
}) %>%
  ggplot() +
  geom_histogram(aes(n), bins=50, col="black", fill="blue") +
  facet_wrap(~ sample) +
  geom_vline(xintercept = 125, col="red")
```

Removing every FOV with fewer than 125 cells

```{r}
keep.smp <- map(cell.data, function(smp) {
  smp %>%
  group_by(fov) %>%
  summarise(n = n()) %>%
  filter(n >= 125) %>%
  pull(fov) %>%
  as.numeric()
})

map_dbl(keep.smp, ~ length(.x))
```

Let's look at the average distance to the direct neighbors per cell per field of view
(per sample).

```{r}
# helper function for nearest neighbors
dist_k_nn <- function(sample, k) {
  nn <- RANN::nn2(sample, eps=0.0, k = k)
  map_dbl(seq_len(nrow(sample)), function(n) {
    mean(nn$nn.dists[n, ])
  })
}

# helper function for getting direct neighbors
get_neighbors <- function(ddobj, id) {
  dplyr::union(
    ddobj$delsgs$ind1[which(ddobj$delsgs$ind2 == id)],
    ddobj$delsgs$ind2[which(ddobj$delsgs$ind1 == id)]
  )
}
```

So the best threshold for the juxtaview may be 100.

```{r}
# map over FOV in each sample
mean.dists.direct.neighbors.smp <- map2(keep.smp, names(keep.smp), function(keep, name) {
  map(keep, function(test.fov) {
    coords <- cell.data[[name]] %>% filter(fov == test.fov) %>%
    select(c(x, y)) %>% as.data.frame
    delaunay <- deldir::deldir(coords)
    dists <- distances::distances(coords)
    map_dbl(seq_len(nrow(coords)), function(id) {
      nn <- get_neighbors(delaunay, id)
      mean(dists[nn, id])
    })
  })
})

map2_dfr(mean.dists.direct.neighbors.smp, names(mean.dists.direct.neighbors.smp), function(dists, name) {
  tibble::tibble(dist = unlist(dists), sample = name)
}) %>%
  ggplot() +
  geom_histogram(aes(dist), bins = 100) +
  lims(x = c(0,200)) +
  geom_vline(xintercept = 100, col = "blue") +
  facet_wrap(~ sample)
```

Furthermore we will look at the distribution of the mean distances to the 
10 -, 20 -, 30 -, and 40 closest cells to get a feeling for which cutoff 
will be used to generate the paraview (just for the first sample!)

It seems like a distance of 180 for the paraview generation might be 
reasonable.

```{r}
neighbor.dists <- map_dfr(keep.smp$CellID_190411, function(test.fov) {
  
  coords <- cell.data$CellID_190411 %>% filter(fov == test.fov) %>%
    select(c(x, y)) %>% as.data.frame
  
  c(10, 15, 20, 30) %>%
    set_names() %>%
    map_dfc(function(k) {
  dist_k_nn(coords, k)
    }) %>%
  set_names(paste0("dist_to_", c("10", "15", "20", "30")))
  
})

neighbor.dists %>%
  pivot_longer(cols = everything()) %>%
  mutate(name = factor(name, 
                       levels = paste0("dist_to_", c("10", "15", "20", "30")))) %>%
  ggplot() +
  geom_histogram(aes(value), bins = 100) +
  facet_wrap(~ name) +
  lims(x = c(0, 300)) +
  geom_vline(xintercept = 180, col = "blue")
```

Calculate the views.

As always we need to make sure that we delete markers with zero variance 
in each view.

```{r}
if ("misty_views.RDS" %in% list.files("data/merfish_benchmark")) {
  misty.views.smp <- readRDS("data/merfish_benchmark/misty_views.RDS")
} else {
  misty.views.smp <- map2(keep.smp, names(keep.smp), function(keep, name) {
    
    misty.views <- map(keep, function(test.fov) {
        
      cell.meta <- cell.data[[name]] %>%
      filter(fov == test.fov)
    
      coords <- cell.meta %>% select(x, y)
    
      ids <- cell.meta$id
    
      expr <- expr.data.norm[[name]][(expr.data.norm[[name]] %>% pull(id)) %in% ids, ] %>%
        select(-id)
    
      # calculate variance per gene
      expr.clean <- expr[, matrixStats::colVars(expr %>% as.matrix) != 0]
    
      create_initial_view(expr.clean) %>%
        add_juxtaview(positions = coords, neighbor.thr = 100) %>%
        add_paraview(positions = coords, l = 180, zoi = 100)
    })
    
    names(misty.views) <- paste0(name, "_fov_", keep)
    
    misty.views
  }) %>%
    unlist(recursive = FALSE)

  saveRDS(misty.views.smp, "data/merfish_benchmark/misty_views.RDS")
}
```

```{r}
length(misty.views.smp)
```

To run MISTy we will only use the 40 most variable genes (controlling for the mean).

```{r}
var.genes <- map_dfr(expr.data.norm, function(expr) {
  expr %>% select(-id)
}) %>%
  pivot_longer(cols = everything()) %>%
  group_by(name) %>%
  summarise(mean = mean(value), var = var(value)) %>%
  mutate(ratio = var / mean) %>%
  slice_max(order_by = ratio, n = 40) %>%
  pull(name)
var.genes
```

Running MISTy

```{r}
if ("ranger_results.RDS" %in% list.files("data/merfish_benchmark")) {
  ranger.results <- readRDS("data/merfish_benchmark/ranger_results.RDS")
} else {
  cv.folds = 10
  ranger.results.folders <- map2(
    misty.views.smp, names(misty.views.smp), function(smp, name) {
      
      sel.genes <- var.genes[var.genes %in% colnames(smp$intraview$data)]
      
      smp %>% run_misty(results.folder = paste0("misty_results/merfish/ranger_", name),
                        cv.folds = cv.folds, model.function = ranger_model, 
                        target.subset = sel.genes)
   })
  ranger.results <- collect_results(ranger.results.folders)
  saveRDS(ranger.results, "data/merfish_benchmark/ranger_results.RDS")
}
```

# Results

What can we actually explain:

```{r fig.width=16}
plot_improvement_stats(ranger.results, measure = "multi.R2")
```

And for which markers to we gain explained variance if we incorporate the
spatial context?

```{r fig.width=16}
plot_improvement_stats(ranger.results, measure = "gain.R2")
```

```{r fig.width=16}
plot_view_contributions(ranger.results)
```

```{r}
plot_interaction_heatmap(ranger.results, view = "para.180", clean = TRUE, cutoff = 0.3)
```


# Appendix

Did we chose the right image size?

Are the cells really overlapping? One possible explanation is that we
have different field of views

```{r}
walk(c(1400, 1500, 1536, 1600), function(img.size) {
  plot <- CellID_190411.pixels %>%
    mutate(x = pixels %% img.size, y = ceiling(pixels / img.size)) %>%
    filter(id %in% c(148290411, 46540411, 52020411)) %>%
    mutate(id = factor(id)) %>%
    ggplot() +
      geom_point(aes(x=x, y=y, col=id), size=.1)
  print(plot)
})
```

Now plot the center of mass on top to check whether this can actually be right.

```{r}
center.mass <- cell.data$CellID_190411 %>%
  filter(id %in% c(148290411, 46540411, 52020411)) %>%
  mutate(id = factor(id)) %>%
  mutate(center_x = x, center_y = y) %>%
  select(c(id, fov, center_x, center_y))

img.size <- 1536
CellID_190411.pixels %>%
  filter(id %in% c(148290411, 46540411, 52020411)) %>%
  mutate(id = factor(id)) %>%
  left_join(center.mass, by="id") %>%
  ggplot() +
    geom_point(aes(x=x, y=y, col=id), size=.1) +
    geom_point(aes(x=center_x, y=center_y, col=id), size=5)
```

# Matlab Code

```{r eval=FALSE}
clear all
close all
ImageSize = 1536; % number of pxls
StepSize = 1394; %pxl; 150/0.1076
XSteps = 13;
YSteps = 15;
EndFrame = 40;
StartFrame =18;
NFOV = 144; % number of fields of views
FileNameForWGA = 'sequential/Cy3_00_';
%%
StartPxl = (ImageSize-StepSize)/2+1; %(1536-1394)/2+1=72
EndPxl = ImageSize-StartPxl+1; % ImageSize-71;
TotalImage = zeros(StepSize*XSteps, StepSize*YSteps);
X = 1-StepSize;
Y = 1;

for jj = 0:NFOV-1
    if NFOV<=10
        FOVid = num2str(jj);
    elseif NFOV>10 && NFOV<=100
        if jj<10
            FOVid = ['0' num2str(jj)];
        else
            FOVid = [num2str(jj)];
        end
    elseif NFOV>100
        if jj<10
            FOVid = ['00' num2str(jj)];
        elseif jj<100
            FOVid = ['0' num2str(jj)];
        else
            FOVid = [num2str(jj)];
        end
    end        
    FileName1 = [FileNameForWGA FOVid];
    [MovieFP, InfoFile] = ReadDax([FileName1, '.dax'],'startFrame', StartFrame, 'endFrame', EndFrame);
    Image1 = mean(MovieFP,3);
    % use adaptive thresholding to get more uniform intensity across filed of view
    Image1 = double(Image1);
    Image1 = Image1 - min(min(Image1));
    Image1 = Image1/max(max(Image1));
    T = adaptthresh(Image1, 0.7,'NeighborhoodSize',33);
    Image1 = Image1./T;
    Min = quantile(Image1(:), 0.4);
    Max = quantile(Image1(:), 0.99);
    Image1 = (Image1-Min)/(Max-Min)*255;
    Image1(find(Image1<0)) = 0;
    Image1(find(Image1>255)) = 255;

    % adjust image oreintation so that they can be correctly stiched
    % together
    Image1(:,1:end) = Image1(:,end:-1:1);
    Image1 = Image1';
    if mod(jj,2*XSteps) == 0 || mod(jj,2*XSteps) == XSteps
        X = X + StepSize;
    elseif mod(jj,2*XSteps) >= 1 && mod(jj,2*XSteps) <= XSteps-1 
        Y = Y + StepSize;
    else
        Y = Y - StepSize;
    end
    Image1 = Image1(StartPxl:EndPxl,StartPxl:EndPxl);

    TotalImage(Y:Y+StepSize-1, X:X+StepSize-1) = Image1;
end

TotalImage = uint8(TotalImage);
figure(1)
imagesc(TotalImage);
axis equal
colormap gray
imwrite(TotalImage,'TotalImage.png')
save('TotalImage.mat','TotalImage');

```
