---
title: "Synthetic"
---

# Set up

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "~/Saez/workflowr_projects/benchmark")
```

Loaded packages.

```{r}
suppressPackageStartupMessages(library(mistyR))
suppressPackageStartupMessages(library(future))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(factoextra))
plan("multisession", workers=14)
```

Loading data

```{r}
data("synthetic")
```

# Introduction

To extend the functionality of MISTy a new API was implemented to model
the different views which are ultimatively combined in a linear meta model.
This analysis is supposed to test how these new models work on real-world 
datasets.

# MISTy Views

```{r}
misty.views.smp <- map(synthetic, function(sample) {
  sample.expr <- sample %>% select(-c(row, col, type))
  sample.pos <- sample %>% select(row, col)
  create_initial_view(sample.expr) %>% add_paraview(sample.pos, l = 10)
})
```

# Running MISTy

Naming our model functions.

```{r}
functions <- c("RF" = ranger_model, "BT" = boosted_trees_model, 
               "NN" = nn_model, "SVM" = svm_model, 
               "MARS" = bagged_earth_model, "LM" = linear_model)
```

Running all functions on all samples on all markers.

```{r}
if ("misty.benchmark.synthetic.RDS" %in% list.files("misty_results")) {
  misty.function <- readRDS("misty_results/misty.benchmark.synthetic.RDS")
} else {
  misty.function <- map2(functions, names(functions), function(fun, fun.name) {
    results.folders <- map2(misty.views.smp, names(misty.views.smp), 
                          function(sample.views, sample.name) {
      run_misty(views = sample.views, 
                results.folder = paste0("misty_results/mibi_tnbc/",
                                        fun.name,"/",sample.name), 
                model.function = fun, seed = 42, cv.folds = 10)
    })
    misty.results <- collect_results(results.folders)
  })
  saveRDS(misty.function, "misty_results/misty.benchmark.synthetic.RDS")
}
```

Collapsing performance results in one tibble.

```{r}
misty.function.performance <- map2_dfr(misty.function, names(misty.function), 
                                       ~ .x$improvements %>% mutate(fun = .y))
```

Comparing the performances.

```{r}
# colors
fun.colors <- c("RF" = "firebrick", "BT" = "blueviolet", "MARS" = "olivedrab",
                "NN" = "steelblue", "SVM" = "orange", "LM" = "darkgoldenrod")
order <- c("RF", "BT", "MARS", "NN", "SVM", "LM")
```

```{r fig.width=12, fig.height=6}
misty.function.performance %>%
  filter(measure == "multi.R2") %>%
  mutate(fun = factor(fun, levels = order), 
         sample = NULL, measure = NULL) %>%
  ggplot() +
  geom_boxplot(aes(x = target, y = value, col = fun)) +
  labs(x = "Target", y = "Multi.R2") +
  scale_color_manual(values = fun.colors)
```

```{r fig.height=8, fig.width=8}
misty.function.performance %>%
  filter(measure == "multi.R2") %>%
  mutate(fun = factor(fun, levels = order), 
         sample = NULL, measure = NULL) %>%
  ggplot() +
  geom_boxplot(aes(x = fun, y = value, col = fun)) +
  labs(x = "Target", y = "Multi.R2") +
  scale_color_manual(values = fun.colors) +
  facet_wrap(~ target, ncol=3, scale="free") +
  theme(axis.text.x = element_blank())
```

Summary statistics

```{r}
misty.function.performance %>%
  filter(measure == "multi.R2") %>%
  mutate(fun = factor(fun, levels = c("RF", "BT", "NN", "SVM", "MARS", "LM")), 
         sample = NULL, measure = NULL) %>%
  group_by(fun) %>%
  summarise(mean.R2 = mean(value), sd.R2 = sd(value)) %>%
  arrange(desc(mean.R2))
```

